TBD

### 2018-10-31 paper/paper.tex
added notebook to make plots for NSF proposal

	The issue of computational expense can be partially overcome either by approximating a GP (often by exploiting the properties of sparse 
	matrices), or by restricting the user to a subset of GPs for which the computation can be sped up. One member of the latter class is the 
	\celerite method, which increases the speed of most common GP computations to $\mathcal{O}(NJ^2)$ where $J$ is typically small compared 
	to $N$. \celerite achieves this increased speed by limiting the user to GPs with a specific functional form of the covariance. Additionally, \celerite 
	only allows for one-dimensional GPs.

>>>>

	The issue of computational expense can be partially overcome either by approximating a GP (often by exploiting the properties of sparse 
	matrices), or by restricting the user to a subset of GPs for which the computation can be sped up. One member of the latter class is the 
	\celerite method, which increases the speed of most common GP computations to $\mathcal{O}(NJ^2)$ where $J$ is typically small compared 
	to $N$. \celerite achieves this increased speed by limiting the user to GPs with a specific functional form of the covariance, albeit a useful and 
	versatile one. Additionally, the \celerite method is only applicable to one-dimensional GPs. Here we present a method to compute a two-dimensional 
	GP on a grid in $\mathcal{O}(NM^3J^2)$ time for an $N\times M$ grid when the covariance in one of the dimensions is described by the \celerite 
	kernel. This is an improvement over the general case in which the computation runs in $\mathcal{O}(N^3M^3)$. Our method is especially useful 
	in cases where $M << N$ and $M$ is constant. In this case the factor of $M^3$ in the runtime can be thought of as a constant. An example would 
	be modeling variability in multiband photometry where $M$ would represent the number of bands and would be small compared to $N$.
